---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# phonewar

<!-- badges: start -->
<!-- badges: end -->

`phonewar` provides a dataset containing peoples iPhone vs Android preferences based on a survey done by tech magazine 'The Hustle' (https://thehustle.co/home/).

## Installation

You can install the phonewar from Github with:

``` r
remotes::install_github("condwanaland/phonedata")
```

## Example

To use `phonewar` first load it

```{r example}
library(phonewar)
## basic example code
```

`phonedata` contains a single dataframe you can load. It contains information about the respondents phone preferences, their reasons for this preference, the city they come from, and metadata about this city (coordinates, population).

```{r}
phones <- phonedata
head(phones)
```

You can check out some graphs of this data

```{r, message=FALSE, dpi=300}
library(dplyr)
library(ggplot2)
library(viridis)
library(tidyr)
phone_sum <- phonedata %>% 
  group_by(phone_type) %>% 
  summarise(n = n()) %>% 
  mutate(freq = n/sum(n))
ggplot(phone_sum, aes(y = phone_type, x = freq, fill = phone_type)) +
  geom_col() +
  geom_text(aes(label = paste0(round(freq, 3), "%"), hjust = 1.2), color = "grey") +
  scale_fill_viridis(discrete = TRUE, option = "turbo")
```

```{r, dpi=300, message=FALSE}
countries <- phonedata %>% 
  group_by(country, phone_type) %>% 
  summarise(n = n()) %>% 
  mutate(freq = n/sum(n)) %>% 
  filter(n > 1) %>% 
  filter(!is.na(country)) %>% 
  select(-n) %>% 
  pivot_wider(names_from = phone_type, values_from = freq, values_fill = 0) %>% 
  mutate(diff = Android - iPhone)

ggplot(countries, aes(y = country, x = diff)) +
  geom_col() +
  labs(caption = "Negative values indicate preference for iPhone, positive for Android",
       x = "Phone preference percentage") +
  theme_bw()
```


## License

The original collectors of this data was 'The Hustle' (https://thehustle.co/home/). The original version of the data can be found here (https://docs.google.com/spreadsheets/d/1UC2I7vO-bS4Qcv0neNRDqJU2qt1Q6ednz8232cmb0_g/edit#gid=430244235).
